Grove: A Convergent Collaborative Structure-Editor~Calculus

### 2020-10-20 grove-paper.tex
Move subcaptions to top and top align subfigures. (Michael D. Adams)
Move subcaptions into main captions (Michael D. Adams)

\tikzset{
  every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level sep=1cm,
  nodes={draw, rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}

@@

%% Title information
\title[Grove]{Grove: A Convergent Collaborative Structure-Editor Calculus}
%\subtitle{Subtitle}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\end{tikzpicture}
TODO: labels for edge numbers

@@

TODO: move subcaptions into master caption

TODO: move subcaptions above figure

TODO: top align subfigures
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

TODO: use mathit instead of var(x)

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
TODO: remove this figure
\caption{User interface}
\label{fig:Construction-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO: delete and leave deleted z8

TODO: delete "x" instead of "y"
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{\autoref{fig:Construction-b} after deleting \Edge{5}}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO: Delete this figure
\newedge{ChangeZ}{R}
\newvertex{ChangeZ}{z}
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vChangeZ" [> "\eChangeZ"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\caption{\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{WrapTimes}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"'] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vChangeZ" [> "\eChangeZ"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\newedge{MoveTimes}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{NestedAlice}{L}
\newvertex{NestedAlice}{w}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{NestedBob}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"],
    "\vMultiChildBob" [> "\eMultiChildBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

Mapping to graph actions

>>>>

\tikzset{
  %every picture/.style={framed, background rectangle/.style={draw=gray!50}},
}
\tikzset{edge style/.style={
  draw,
  font={\small\ttfamily},
  /tikz/every edge quotes/.style={
    %draw=gray!20,
    anchor=west,
    swap/.append code={
      \ifpgfarrowswap
        \pgfkeysalso{anchor=west}
      \else
        \pgfkeysalso{anchor=east}
      \fi}},
}}
\tikzset{graphs/graph style/.style={
  tree layout,
  level sep=1cm,
  nodes={draw, rounded corners=1mm},
  edges={edge style},
}}
\tikzset{graphs/root style/.style={
 %draw=none,
 as={\textbullet$_{0}$}
}}

@@

%% Title information
\title[Grove]{Grove: A Convergent Collaborative Structure-Editor~Calculus}
%\subtitle{Subtitle}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\end{tikzpicture}

TODO: labels for edge numbers

@@

TODO: move subcaptions into master caption
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole.
\autoref{fig:A simple tree with a hole-a}:~User interface.
\autoref{fig:A simple tree with a hole-b}:~Graph representation.}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\columnwidth}
\centering
\caption{}
\label{fig:Construction-a}
TODO: remove this figure
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\columnwidth}
\centering
\caption{}
\label{fig:Construction-b}
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction.
\autoref{fig:Construction-a}:~User interface.
\autoref{fig:Construction-b}:~\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}.}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:Change-a}
TODO: delete and leave deleted z8

TODO: delete "x" instead of "y"
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:Change-b}
TODO: Delete this figure
\newedge{ChangeZ}{R}
\newvertex{ChangeZ}{z}
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vChangeZ" [> "\eChangeZ"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change.
\autoref{fig:Change-a}:~\autoref{fig:Construction-b} after deleting \Edge{5}.
\autoref{fig:Change-b}:~\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}.}
\label{fig:Change}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Wrapping-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Wrapping-b}
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Wrapping-c}
\newedge{WrapTimes}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"'] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vChangeZ" [> "\eChangeZ"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping.
\autoref{fig:Wrapping-a}: \autoref{fig:Change-b} after deleting \Edge{1}.
\autoref{fig:Wrapping-b}:~\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}.
\autoref{fig:Wrapping-c}:~\autoref{fig:Wrapping-b} after adding \Edge{9}.
}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:Move-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.45\linewidth}
\centering
\caption{}
\label{fig:Move-b}
\newedge{MoveTimes}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}.
\autoref{fig:Move-a}:~\autoref{fig:Wrapping-c} after deleting \Edge{9}.
\autoref{fig:Move-b}:~\autoref{fig:Move-a} after adding \Edge{11}.}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Different Parts of the Code-a}
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Different Parts of the Code-b}
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Different Parts of the Code-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code.
\autoref{fig:Editing Different Parts of the Code-a}:~\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}.
\autoref{fig:Editing Different Parts of the Code-b}:~\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}.
\autoref{fig:Editing Different Parts of the Code-c}:~The
result of merging \autoref{fig:Editing Different Parts of the Code-a}
with \autoref{fig:Editing Different Parts of the Code-b}.}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Nested Parts of the Code-a}
\newedge{NestedAlice}{L}
\newvertex{NestedAlice}{w}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Nested Parts of the Code-b}
\newedge{NestedBob}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.32\linewidth}
\centering
\caption{}
\label{fig:Editing Nested Parts of the Code-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code.
\autoref{fig:Editing Nested Parts of the Code-a}:~\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}.
\autoref{fig:Editing Nested Parts of the Code-b}:~\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}.
\autoref{fig:Editing Nested Parts of the Code-c}:~The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}.}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.24\linewidth}
\centering
\caption{}
\label{fig:Multi-child-a}
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.24\linewidth}
\centering
\caption{}
\label{fig:Multi-child-b}
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.24\linewidth}
\centering
\caption{}
\label{fig:Multi-child-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"],
    "\vMultiChildBob" [> "\eMultiChildBob"]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.24\linewidth}
\centering
\caption{}
\label{fig:Multi-child-d}
TODO: show UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts.
\autoref{fig:Multi-child-a}:~\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO.
\autoref{fig:Multi-child-b}:~\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO.
\autoref{fig:Multi-child-c}:~The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}.
\autoref{fig:Multi-child-d}:~User interface showing the multi-child conflict in \autoref{fig:Multi-child-c}.}
\label{fig:Multi-child}
\end{figure*}

@@

Mapping to b actions
